Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm

### 2019-09-24 paper/virtual_cytoplasm_v2.tex
plots improved

\begin{figure}[H]
\includegraphics[scale=0.5]{msd.pdf}
\includegraphics[scale=0.5]{diff_cyto_over_singles.pdf}
\caption{A)Diffusion coefficient of crowders from single molecule simulations (blue bars) and cytoplasm simulations (orange bars). B) The ratio between diffusion coefficient obtained from cytoplasm to single molecule simulations. The crowders are sorted according to their sizes on the x-axis. \textbf{\color{red}{THE Dcyto/Ddil PLOT IS "SQUEEZED" BECAUSE OF ITS STRANGE SCALE. IT WOULD BE BETTER TO CENTER THE DATAPOITS, E.G. USE THE Y-AXIS RANGE OF 0.0-0.2 OR SOMETHING SIMILAR. THIS SCALE WILL MAKE THE DIFFERENCE OF THE BEHAVIOR OF tRNA MORE VISIBLE AS WELL}}}
\label{fig:translational_diffusion}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[scale=0.5]{rdf_RNA_metabolites.pdf}
\caption{Radial distribution function showing the probability of finding metabolites or cations around RNA molecules in the cytoplasm model.\color{red}\textbf{THIS PLOT NEEDS REVISION. I DON'T SEE ERROR BARS (HOW WAS STATISTICS DONE FOR THE RDFs?).I SUBMITTED NEW RDF CALCULATIONS CENTERED AROUND tRNA BECAUSE I DIDN'T FIND THE XVG FILES THAT WERE USED TO GENERATE THIS PLOT}}
\label{fig:tRNA_aggregation}
\end{figure}

@@

\caption{A) Solvent accessible surface area (sasa) for 8 proteins from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). The average sasa for each protein in single molecule simulation is over number of chains of proteins and three replica. The average sasa for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors. B) Root mean squared displacement (rmsd) for 8 proteins from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). The average rmsd for each protein in single molecule simulation is over number of chains of proteins and three replica. The average rmsd for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors.\textbf{\color{red}{THE MEASUREMENT NAME, SASA AND RMSD, IS MISSING IN THE Y-AXIS OF BOTH PLOTS}}}
\label{fig:structural_integrity_chain}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[scale=0.5]{rmsf_2cols.pdf}
\caption{Root mean squared fluctuations (rmsf) for 8 crowders from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). x-axis shows the residues for each chain of proteins. The average rmsf for each protein in single molecule simulation is over number of chains of proteins and three replica. The average rmsd for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors.\textbf{\color{red}{CAN YOU ADD THE PROTEIN NAME AS A LABEL INSIDE EACH PLOT? I THINK THE VARIABLE NAME SHOULD BE IN THE Y-AXIS (RMSF NM2)}}}
\label{fig:rmsf}
\end{figure}

>>>>

\begin{figure}[H]
\includegraphics[scale=0.5]{msd.pdf}
\includegraphics[scale=0.5]{diff_cyto_over_singles.pdf}
\caption{A)Diffusion coefficient of crowders from single molecule simulations (blue bars) and cytoplasm simulations (orange bars). B) The ratio between diffusion coefficient obtained from cytoplasm to single molecule simulations. The crowders are sorted according to their sizes on the x-axis.}
\label{fig:translational_diffusion}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[scale=0.5]{rdf_RNA_metabolites.pdf}
\caption{Radial distribution function showing the probability of finding metabolites or cations around RNA molecules in the cytoplasm model.\color{red}\textbf{I SUBMITTED NEW RDF CALCULATIONS CENTERED AROUND tRNA BECAUSE I DIDN'T FIND THE XVG FILES THAT WERE USED TO GENERATE THIS PLOT}}
\label{fig:tRNA_aggregation}
\end{figure}

@@

\caption{A) Solvent accessible surface area (sasa) for 8 proteins from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). The average sasa for each protein in single molecule simulation is over number of chains of proteins and three replica. The average sasa for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors. B) Root mean squared displacement (rmsd) for 8 proteins from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). The average rmsd for each protein in single molecule simulation is over number of chains of proteins and three replica. The average rmsd for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors.}
\label{fig:structural_integrity_chain}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[scale=0.5]{rmsf.pdf}
\caption{Root mean squared fluctuations (rmsf) for 8 crowders from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). x-axis shows the residues for each chain of proteins. The average rmsf for each protein in single molecule simulation is over number of chains of proteins and three replica. The average rmsd for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors.\textbf{\color{red}{CAN YOU ADD THE PROTEIN NAME AS A LABEL INSIDE EACH PLOT? I THINK THE VARIABLE NAME SHOULD BE IN THE Y-AXIS (RMSF NM2)}}}
\label{fig:rmsf}
\end{figure}
